A Mechanised Library for Generic (Co)Programming

### 2024-02-01 paper/paper.tex
Implementation of rsfc into hylo

>>>>

\paragraph{Implementation into hylomorphisms}
In order to implement rsfcs as hylos we need a
parametric distributive law
\[
  \lambda_{X} : GG_{\infty}X \to G_{\infty}GX
\]
This can be defined as $\lambda = G_{\infty}G(\head) \comp \anacofree{G(\tail)}$.
The distributive law is instrumental to be able to lift coalgebras in the
following sense. Give a $G$-coalgebra on $X$, a lifting $H$ is a functor which
lifts this coalgebra to a $G$-coalgebra on $HX$.  In particular, the lifting
$G_{\lambda}$ takes $G_{\infty}$-coalgebras on $X$ and transforms them into
$G_{\infty}$-coalgebras on $GX$
\begin{align*}
  & G_{\lambda}(c) : GA \to G_{\infty} GA\\
  & G_{\lambda}(c) = \lambda \comp G (c)
\end{align*}
where $c : C \to GC$.

Now, given an algebra $a : GG_{\infty} A \to A$ on the carrier $A$ we can
convert it into an algebra for the carrier $G_{\infty} A$ by
\begin{align*}
  & \floor{a} : GG_{\infty} A \to G_{\infty} A\\
  & \floor{a} = G_{\infty}(a) \comp \anacofree{G_{\lambda}(\delta)}
\end{align*}
where $\eta_{A} : A \to G_{\infty} A$ is the unit of the comonad creating an
infinite constant list.

At this point the hylo is simply defined by
$\hylo{\InOp}{a} : \mu F \to G_{\infty}A$  and the rsfc is derived as follows
\begin{align*}
  & \operator{rsfc} : \mu G \to A \\
  & \operator{rsfc} = \head \comp \hylo{\InOp}{a}
\end{align*}
